### 2020-07-29 draft.Rmd

We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial. We conclude using Kruskal-Wallis tests that SEED accounts had more savings than the other two groups. Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].

@@

If we were doing a pairwise comparison test to determine the existance of a difference, we would use Bonferroni's adjustment for the paired tests to control for type one error. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins].  However, we will only be using the pairwise comparison after the k-sample Kruskal-Wallis test, so we do not need to be concerned with it here.

@@

as.table(m <= alpha) %>%
  kable(caption = "Significant difference found in
        pairwise comparison with Wilcoxon Test.")

@@

Tables 4 and 5 show a significant difference in three one-sided comparisons tests. We can reasonably conclude that the SEED accounts perform better than the control groups and the marketing treatment. However, it is worth noting that if we used the Bonferroni adjustment for alpha, we would only mark a significant difference between the seed and control groups.

@@

In most cases, the conclusions of our tests aligned with the original paper. In section 3 we conclude that the SEED accounts are effective savings mechanisms, agreeing with the original authors. In section 4 we conclude that there is a difference between the three different treatments, but make a note that depending on the significance level employed we have reason to doubt that there is a difference between the marketing treatment and the SEED accounts. The tests concluded a difference, but further study is warranted. In section 5 we used different regression techniques from the original paper, as the authors had done a good bit of massaging to make OLS work. While the nonparametric methods did conclude statistical significance of the SEED treatments over the marketing treatments, the coefficients determined by the methods were significantly lower. Leading us to conclude that while there is a statistically significant effect of the SEED accounts on savings compared to the marketing treatment, there is not necessarily a practically significant effect.

>>>>

We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial. We conclude using Kruskal-Wallis tests that there exists a difference within the three groups. Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].

@@

To control for type one error we will use Bonferroni's adjustment for the paired tests. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins].

@@

as.table(m <= adjusted_alpha) %>%
  kable(caption = "Significant difference found in
        pairwise comparison with Wilcoxon Test.")

@@

Tables 4 and 5 show a significant difference in the SEED accounts versus the control group. Therefore, we can reasonably conclude that the SEED accounts perform better than the control group. However, it is worth noting that under the Bonferroni adjustment for alpha, we do not mark a significant difference between marketing and control, or SEED and marketing.

@@

In most cases, the conclusions of our tests aligned with the original paper. In section 3 we conclude that the SEED accounts are effective savings mechanisms, agreeing with the original authors. In section 4 we conclude that there is a difference within the three treatments, but we make a note that we could not determine a significant difference between the SEED accounts and the marketing group. The tests concluded a difference overall, but further study is warranted. In section 5 we used different regression techniques from the original paper, as the authors had done a good bit of massaging to make OLS work. While the nonparametric methods did conclude statistical significance of the SEED treatments over the marketing treatments, the coefficients determined by the methods were significantly lower. Leading us to conclude that while there is a statistically significant effect of the SEED accounts on savings compared to the marketing treatment, there is not necessarily a practically significant effect.
